Compositional Equivalences Based on Open pNets

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
played with indices

We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
We use ${\displaystyle \bigodot_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=-1}^{0} \Post_i}$ is the identity.

@@

\begin{lem}[Alternative definition of weak open transitions]
\label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
    \mathcal{T}\myrangle$ be an open automaton and $\mylangle J,\mathcal{S}, s_0,V_2,
    \WT\myrangle$ be the
weak open automaton derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq -1$, $m\geq -1$ s.t.\footnote{$n=-1$ (resp. $m=-1$) corresponds to the case where there is no $\tau$ transition before (resp. after) the transition $\alpha$.}:

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [0..n].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=n}^{0}\Post_{1j}}}\\
s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\bigoplus_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \oplus}\\
{}~\qquad \displaystyle{\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{0}\Post_{1j}}\land\\ 
{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}}\Big)\\
\Post=\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}
$

\end{enumerate}
\end{lem}
\begin{proof}
 ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
\begin{itemize}
\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule \WTDeux\ we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$. Induction step is to infer that formula holds for transitions of length  $n+1$. 
We consider the case $n'=n+1$.  We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$). In other words, we consider the sequence of ($n+m+4$) open transitions: 
\begin{mathpar}
\Big(\forall i \in [0..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
\Big) 
\end{mathpar}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \Rightarrow\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
\begin{align*}
s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{1}\!\!\Post_{1j}}}\\
\set{\gamma}=&\bigoplus_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
& \bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }\\
\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}
\end{align*}

We need to prove that   by adding the following open transition the implication remains true:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta_{10}},\Pred_{10},\Post_{10}}
         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
\end{mathpar}
First by using rule \WTDeux~ we have:
\begin{mathpar}

 \openrule
         {
           \set{\beta_{10}},\Pred_{10},\Post_{10}}
         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
\Rightarrow 
{ \openrule
       {
           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
}
\end{mathpar}

@@

\begin{mathpar}
\inferrule {\openrule
       {
           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
\\
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
\\
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
\\\\
\set{\gamma''}= \vis{\set{\beta_{10}}} \oplus \set{\gamma}\subst{\Post_{10}}\\
\Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
\Post\,''=\Id(s'')\shortodot\Post\shortodot\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
} \WTTrois
\end{mathpar}
where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
\begin{align*}
s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\alpha''=&\alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigodot_{j=n+1}^{0}\Post_{1j}}\\
\set{\gamma''}=&\bigoplus_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
&\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
\\
\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{0}\Post_{1j}}\land\\ 
&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}}\Big)
\\
\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}
\end{align*}

@@

These two cases above prove the implication with $n=-1$ and $m=-1$.

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+3$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\Rightarrow \,
 \forall i \in [0..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
\displaystyle{\set{\gamma_1}= \bigoplus_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1 j} } }} \\
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{0} \subst{\Post_{1i}} 
$

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [0..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where
\begin{mathpar}
s''=s_{30}

@@

\displaystyle{\set{\gamma_3}= \bigoplus_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{3 j} } }}

@@

\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigodot_{j=i-1}^{0}\Post_{3 j}} )

@@

 \Post_3= \bigodot_{i=m_1}^{0} \subst{\Post_{3i}} 
\end{mathpar}

\item Concerning the middle reduction, by induction hypothesis there exists a set of open transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
\Rightarrow 
\bigg(\forall i \in [0..n_2].\openrule
    {
       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [0..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}

>>>>

We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
We use ${\displaystyle \bigodot_{i=n}^{1} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=0}^{1} \Post_i}$ is the identity.

@@

\begin{lem}[Alternative definition of weak open transitions]
\label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
    \mathcal{T}\myrangle$ be an open automaton and $\mylangle J,\mathcal{S}, s_0,V_2,
    \WT\myrangle$ be the
weak open automaton derived from $A$.  The two following statements are equivalent
%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
\begin{enumerate}
\item Either $   
\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq 0$, $m\geq 0$ s.t.\footnote{$n=0$ (resp. $m=0$) corresponds to the case where there is no $\tau$ transition before (resp. after) the transition $\alpha$.}:

\begin{mathpar}
%\mprset {vskip=.5ex}
%\inferrule 
\forall i \in [1..n].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [1..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \end{mathpar}
\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
 \begin{mathpar}
%   \Longleftrightarrow  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
%}
\end{mathpar}
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=n}^{1}\Post_{1j}}}\\
s=s_{11} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\bigoplus_{i=1}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{1}\Post_{1j}}} \oplus}\\
{}~\qquad \displaystyle{\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{1}\Post_{1j}}\land\\ 
{}~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}}\Big)\\
\Post=\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}
$

\end{enumerate}
\end{lem}
\begin{proof}
 ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=0$, $n=0$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
\begin{itemize}
\item The base case there is one transition, so $n=0$ and $m=0$, we have:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}
%}
\end{mathpar} 
by rule \WTDeux\ we can directly conclude the implication: 
 \begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
% \openrule
%         {
%           \set{\beta},\Pred,\Post}
%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
%}

\openrule
         {
           \set{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
{ \openrule
         {
           \vis{\set{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
\end{mathpar} 
\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$. Induction step is to infer that formula holds for transitions of length  $n+1$. 
We consider the case $n'=n+1$.  We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$). In other words, we consider the sequence of ($n+m+2$) open transitions: 
\begin{mathpar}
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\quad \wedge\\
~~\qquad\qquad\forall i \in [1..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
\Big) 
\end{mathpar}

@@

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [2..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
{}~~\hspace{2.25cm}\forall i \in [1..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \Rightarrow\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
\begin{align*}
s''=s_{12} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
\alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{2}\!\!\Post_{1j}}}\\
\set{\gamma}=&\bigoplus_{i=2}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{2} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{2}\Post_{1j}}} \oplus\\
& \bigoplus_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }\\
\Pred=&\bigwedge_{i=2}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{2}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{2}\Post_{1j}}\land\\ 
&\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=&\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{2}\Post_{1j}
\end{align*}

We need to prove that   by adding the following open transition the implication remains true:
\begin{mathpar}
 % \mprset {vskip=.5ex}
%\inferrule{
 \openrule
         {
           \set{\beta_{11}},\Pred_{11},\Post_{11}}
         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}%}
\end{mathpar}
First by using rule \WTDeux~ we have:
\begin{mathpar}

 \openrule
         {
           \set{\beta_{11}},\Pred_{11},\Post_{11}}
         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}
\Rightarrow 
{ \openrule
       {
           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{11}
				 } {s_{11} \OTWeakarrow {\tau}s_{12}} \in \WT
}
\end{mathpar}

@@

\begin{mathpar}
\inferrule {\openrule
       {
           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{1}
				 } {s_{11} \OTWeakarrow {\tau}s_{12}}\! \in\! \WT
\\
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
\\
\openrule
         {
          \emptyset,\True,\Id(s'')
				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
\\\\
\set{\gamma''}= \vis{\set{\beta_{11}}} \oplus \set{\gamma}\subst{\Post_{1}}\\
\Pred\,''\!=\!\Pred_{11}\land\Pred\subst{\Post_{11}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{11}}
\Post\,''=\Id(s'')\shortodot\Post\shortodot\Post_{11} \\ \alpha''=\alpha'\subst{\Post_{11}}
}
{
\openrule
         {
          \set{\gamma''}, \Pred\,'',\Post\,''
				 } 
         {s_{11} \OTWeakarrow {\alpha''} s'} \in\!\WT
} \WTTrois
\end{mathpar}
where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
\begin{align*}
s_{11}=s_{11} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
\alpha''=&\alpha\subst{\bigodot_{j=n+1}^{2}\Post_{1j}}\subst{\Post_{11}} = \alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\\
\set{\gamma''}=&\bigoplus_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
&\bigoplus_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }
\\
\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
&\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)
\\
\Post=&\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}
\end{align*}

@@

These two cases above prove the implication with $n=0$ and $m=0$.

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s'} \in\! \WT 
\Rightarrow \,
 \forall i \in [1..n_1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
\end{mathpar}
where \\
$ 
s=s_{11} \wedge s_{1{(n_1+1)}}\!=s',\quad
\displaystyle{\set{\gamma_1}= \bigoplus_{i=1}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1 j} } }} \\
\Pred_1\!=\!\bigwedge_{i=1}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{1}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{1} \subst{\Post_{1i}} 
$

\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
\begin{mathpar}
%\inferrule{
\openrule
         {
           \set{\gamma_3},\Pred_3,\Post_3   }
         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
\Rightarrow\, 
\forall i \in [1..m_1].\openrule
    {
       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
\end{mathpar}
where
\begin{mathpar}
s''=s_{31}

@@

\displaystyle{\set{\gamma_3}= \bigoplus_{i=1}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{1} \Post_{3 j} } }}

@@

\Pred_3\!=\!\bigwedge_{i=1}^{m_1}(\Pred_{3i} \subst{\bigodot_{j=i-1}^{1}\Post_{3 j}} )

@@

 \Post_3= \bigodot_{i=m_1}^{1} \subst{\Post_{3i}} 
\end{mathpar}

\item Concerning the middle reduction, by induction hypothesis there exists a set of open transitions in $\mathcal{T}$ such that:
\begin{mathpar}
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
\Rightarrow 
\bigg(\forall i \in [1..n_2].\openrule
    {
       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge
\forall i \in [1..m_2].\openrule
         {
           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
\bigg)         
\end{mathpar}

where
\begin{align*}
s'=s_{21} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{21}' \wedge s_{2(m_2+1)}'=s''\\
\alpha''=&\alpha'\subst{\bigodot_{j=n_2}^{1}\Post_{2j}}\\
\set{\gamma_2}=&\bigoplus_{i=1}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{1} \Post_{2 j} } }  \oplus  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{1}\Post_{2j}}} \oplus\\
&
 \bigoplus_{i=1}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{1}\Post_{2j}}}
\\
\Pred_2=&\bigwedge_{i=1}^{n_2}\Pred_{2i}\subst{\bigodot_{j=i-1}^{1}\Post_{2j}}\land\Pred\,' \subst{\bigodot_{j={n_2}}^{1}\Post_{2j}}\land\\ 
&\Big(\bigwedge_{i=1}^{m_2}\Pred\,'_{2i}\subst{\bigodot_{j=i-1}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{1}\Post_{2j}}\Big)\\
\Post_2=&\bigodot_{j=m_2}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{1}\Post_{2j}
\end{align*}

\end{enumerate}
~~\\
Therefore, we can deduce that we have:
\begin{mathpar}
{ \openrule
         {
           \set{\gamma}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
 \Rightarrow
\bigg(\forall i\in [1..(n_1\!+\!n_2)].\openrule
    {
       \set{\beta_{4i}},\Pred_{4i},\Post_{4i}   }
         {s_{4i} \OTarrow {\tau} s_{4(i+1)}} \in\mathcal{T} \wedge

\openrule
         {
           \set{\beta'},\Pred\,',\Post\,' }
         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
\wedge\,
\forall i \in [1..(m_1\!+\!m_2)].\openrule
         {\set{\beta_{5i}},\Pred_{5 i},\Post_{5i}    }
         {s_{5i}\OTarrow {\tau} s_{5({i+1})}}\in\mathcal{T}\bigg)  
\end{mathpar}
